\documentclass[10pt]{article}
\usepackage[english]{babel}
\usepackage{xcolor}
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.5}
\usepackage{hyperref}
\input{config/minimal-resume-config}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=darkblue,
}
\begin{document}

\begin{center}
	{\fontsize{\sizeone}{\sizeone}\fontspec[Path = fonts/,LetterSpace=15]{Montserrat-Regular} ABHISHEK CHOUDHARY}
	\\
	\vspace{2mm}
	{\fontsize{1em}{1em}\fontspec[Path = fonts/]{Montserrat-Light}
\href{mailto:choudharyabhishek2199@gmail.com}{Email} ~|~
\href{https://linkedin.com/in/av1choudharyy}{LinkedIn} ~|~
\href{https://github.com/av1choudharyy}{GitHub} ~|~
\href{tel:+918294817554}{Mobile}
}
	\\
	\vspace{2mm}
	{\fontsize{0.95em}{1.2em}\fontspec[Path = fonts/]{CrimsonText-Regular}
	Full-stack engineer specializing in AI-powered platforms, agentic systems, and scalable distributed architectures. 4+ years building production systems from LLM-driven intelligence platforms to high-performance backend systems.
	}
\end{center}

\vspace{-6mm}

\chap{EXPERIENCE}{

\job
	{\href{https://aryra.in}{Aryra}}
	{Mar 2025 – Present}
	{Founder}
	{aryra.in}
	{\begin{newitemize}
        \format{Custom ReAct Agent \& Provider Abstraction}{Custom agent loop with 33 tools and no LangChain/LangGraph dependency, with real-time SSE streaming of reasoning, tool calls, and inline Plotly charts. Unified provider abstraction — single env var switches entire cloud stack (AWS: S3+Textract+Bedrock+Transcribe; GCP: GCS+Vision+Vertex+Google Transcribe) with per-service overrides. LLM router supports Anthropic, AWS Bedrock, Google Vertex, OpenAI, and Ollama under a single interface.}
        \format{Knowledge Bank, Semantic Search \& HNSW}{pgvector semantic search with HNSW indexing for sub-millisecond nearest-neighbor lookup and HyDE query expansion. Auto-caches every Q\&A pair as vector embeddings for progressive knowledge enrichment. Knowledge graph interlinking queries, tables, and files with schema-aware context enrichment and 24-hour TTL cache.}
        \format{Multimodal Asset Analysis \& Inline Generation}{Every asset analyzed inline in chat: image OCR (Textract or Cloud Vision), PDF page-level extraction with per-page embeddings (PyMuPDF), Excel chunked processing, audio transcription (AWS or Google), and video analysis via native Bedrock Converse video blocks (s3Location, Nova Pro). Image and video generation via abstract GenerationProvider (Bedrock, OpenAI DALL-E, Google Imagen) — generated files streamed directly into chat.}
        \format{File Management, Caching \& Observability}{SHA-256 hash-based file deduplication across S3/GCS, proxied downloads (zero direct URL exposure), semantic file search, and storage lifecycle tiering. Redis cache abstraction with NullCacheBackend fallback and TTL-aware schema deduplication. Self-hosted observability: OpenTelemetry (FastAPI + asyncpg instrumented) → Grafana Alloy → Loki + Tempo + Prometheus + Grafana dashboards.}
        \format{Session Management \& Collaboration}{Session forking from any message, token-based sharing with message boundaries, fork chain traversal, bookmarks, and real-time SSE notification stream. React 19 / TanStack Start SSR frontend with Zustand, pnpm monorepo + Turborepo, deep linking, and React Native/Expo mobile app with push notifications.}
        \format{Enterprise Security — IAM-Style RBAC \& NL2SQL}{JWT auth with refresh rotation and bcrypt hashing. IAM-style RBAC with JSON policy documents, deny-wins evaluation, role hierarchy, and wildcard resource matching across 8 resource groups with 18 admin API endpoints. NL2SQL with automatic schema discovery, TTL-cached metadata, and 20+ SQL injection pattern blocks.}
        \format{Sandboxed Execution \& Integrations}{Python sandbox with subprocess isolation, 120s timeout, and custom MetaPathFinder blocking 18 dangerous imports. Inline Plotly chart rendering via SSE, Excel/PDF/PPTX/CSV export. Gmail OAuth (12 tools, multi-account), SearXNG + Crawl4AI web search, Google SSO, and persistent per-user memory auto-injected into agent context.}
	\end{newitemize}}

\job
	{Piping Rock India}
	{Mar 2025 – Present}
	{Senior Software Consultant}
	{Bangalore, IN}
	{\begin{newitemize}
        \format{AI Asset Analysis Pipeline}{Built hybrid OCR + Vision API combining AWS Textract with Claude Sonnet 4.5 (Bedrock) for semantic image understanding. Engineered 3-tier product matching using Amazon Titan V2 embeddings (1024-dim cosine similarity): image OCR vectors, description vectors, and keyword fallback, with LLM-in-the-loop visual verification and confidence scoring. Supports PDF page-level processing, image compression, and pre-signed S3 URL generation.}
        \format{Agentic RAG Platform}{Designed enterprise AI platform using LangGraph ReAct agent with 16 orchestrated tools across Claude Haiku 4.5 and Sonnet 4.5 via AWS Bedrock cross-region inference. Built multimodal embedding pipeline with Amazon Nova Embed V2 (3072-dim) for semantic indexing across images, PDFs, and documents.}
        \format{Multimodal Document Intelligence}{Engineered unified analysis pipeline: image OCR (Textract primary, Claude Vision fallback), PDF page-level extraction with per-page embeddings (PyMuPDF, adaptive DPI), Excel chunked processing (openpyxl), audio transcription (Amazon Transcribe), and video analysis (ffmpeg keyframe extraction + Claude Vision batch frame descriptions).}
	\end{newitemize}}

	\job
	{Headout}
	{Mar 2025 – Oct 2025}
	{Senior Software Engineer}
	{Bangalore, IN}
	{\begin{newitemize}
        \format{Review Collection \& A/B Testing}{Architected and executed comprehensive A/B testing framework for review incentivization UI experiments across web and mobile platforms, successfully scaling to 1.5 million users and increasing review submission rate by 11.4\% through data-driven iteration.}
        \format{WhatsApp Business Integration}{Designed and implemented end-to-end WhatsApp Business API integration for review collection using Flow APIs, including webhook processing, cryptographic validation, template management, and media handling infrastructure, achieving 7.3\% increase in collection rate and boosting booking rates by 7\%.}
        \format{Full-Stack Project Leadership}{Took complete ownership of review and rating project from conception to production, managing backend API architecture (Kotlin microservices, Redis caching), frontend experimentation framework, analytics integration with Mixpanel, and cross-functional coordination with product and design teams.}
        \format{Team Leadership \& Code Quality}{Mentored new interns and engineers to accelerate growth. Rapidly resolved critical P0/P1 bugs, conducted thorough PR reviews for major releases, and collaborated with UX/PM to resolve UI roadblocks, improving team efficiency and reducing development time.}
	\end{newitemize}}

	\job
	{Cimpress}
	{Dec 2023 – Mar 2025}
	{Software Engineer}
	{Mumbai, IN}
	{\begin{newitemize}
		\format{UI Common Components}{Led epic for developing reusable UI components for Order Management System. Coordinated subgroup to parallelize tasks, ensuring team alignment and streamlining component deployment.}
		\format{Postgres Query Optimization}{Optimized stored procedures for Postgres 15, improving performance by 1.4x to 27x. Reduced query response times from 26 seconds to under 1 second by replacing CTEs with joins.}
		\format{Order Management API Design}{Led Epic to design and implement APIs for order creation, validation, rejection, cancellation and search, ensuring seamless integration across the entire flow.}
		\format{Entity Traceability System}{Designed traceability system with DocumentDB schema for dynamic attribute search. Established entity relationships for real-time tracking across distributed systems.}
		\format{Legacy System Integration}{Integrated traceability system with legacy infrastructure using integration wrappers, ensuring smooth transition and graceful retirement.}
	\end{newitemize}}

	\job
	{Piping Rock}
	{Jan 2022 – Dec 2023}
	{Software Developer}
	{Bangalore, IN}
	{\begin{newitemize}
        \format{Database Pool Manager}{Designed pool manager for database connections across multiple servers with varying access levels. Improved application load times by 20\% by reusing connections and reducing overhead.}
        \format{Warehouse Management System}{Designed and deployed React/Node.js WMS on AWS, optimizing bottle ordering, manufacturing, and scheduling, reducing operational costs.}
        \format{Batch Scheduling Automation}{Automated batch scheduling with drag-and-drop React interface, improving efficiency and reducing labor costs by 33\%.}
        \format{Custom ORM}{Created custom ORM handling SQL queries via JSON, streamlining business logic execution and preventing deadlocks with single execution point.}
        \format{WebSocket Microservice}{Led development of WebSocket-based microservice with API Gateway and DynamoDB, improving real-time communication and workflow efficiency by 1.3x.}
        \format{React UI Libraries}{Developed search/autocomplete libraries with React hooks, integrated throttling and debouncing, and authored technical documentation.}
	\end{newitemize}}

}

\chap{SKILLS}{
	\begin{newitemize}
		\format{AI \& ML}{LangGraph, ReAct Agents, RAG, HNSW Vector Search, Prompt Engineering, Multimodal Embeddings, NL2SQL, LLM-in-the-Loop Verification}
		\format{AI Services}{AWS Bedrock (Claude Sonnet 4.5, Claude Haiku 4.5), Amazon Nova Embed V2, Amazon Titan V2, Amazon Rerank 1.0, AWS Textract, Amazon Transcribe}
		\format{Languages}{Python, JavaScript, TypeScript, Kotlin, SQL, NoSQL, HTML, CSS}
		\format{Frameworks}{FastAPI, React.js, React Native, Node.js, Express.js, Next.js, Nest.js, Spring Boot, Expo}
		\format{Databases}{SQL Server, PostgreSQL, MySQL, MongoDB, DocumentDB, DynamoDB, Vector Databases (hnswlib)}
		\format{Tools \& Cloud}{AWS (Lambda, S3, Bedrock, Fargate, EC2, CloudFront, CloudFormation, SAM, Route 53, CloudWatch), Docker, Git, CI/CD, JIRA}
		\format{Architecture}{Agentic AI Systems, Microservices, REST APIs, SSE Streaming, WebSockets, Event-Driven, Distributed Systems, Serverless}
	\end{newitemize}
}
\end{document}
